---
title: "Plant schisto LTs"
author: "DJC"
date: "11/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Code for analysis of plant schisto LTs
Here, we analyze the data using the final length and weekly averages of eggs and cercs as response variables, following methods from Civitello and Hartman 2020, Ecology and Johnson et al. 2014, Proc B, specifically just calculating weekly averages of egg laying and cerc shedding.

```{r packages, message=FALSE}
library(dplyr)
library(glmmTMB)
library(ggplot2)
library(cowplot)
library(emmeans)
library(stringr)
theme_set(theme_cowplot())
```


```{r data}
Asher_lt = read.csv("C:/RData/Dan Dissertation/Detritus LTs/WH_decomp_LT.csv")
Asher_lt[,"Food"][which(Asher_lt[,"Food"] == "Good (chicken) ")] = "Lab food"
Asher_lt[,"Food"][which(Asher_lt[,"Food"] == "3 week")] = "21 days"
Asher_lt[,"Food"][which(Asher_lt[,"Food"] == "7 week ")] = "49 days"
Asher_lt[,"Food"][which(Asher_lt[,"Food"] == "2 day")] = "2 days"

Asher_lt[,"Status"] = ifelse(Asher_lt[,"Alive"]==0, 1, 0)


L_max = aggregate(Length ~ Snail, FUN=max, data=Asher_lt)
C_tot = aggregate(Cerc ~ Snail, FUN=sum, data=Asher_lt, drop=F)
E_tot = aggregate(Eggs ~ Snail, FUN=sum, data=Asher_lt)
Surv = aggregate(Alive ~ Snail, FUN=sum, data=Asher_lt)
Censored = aggregate(Status ~ Snail, FUN=max, data=Asher_lt)
Infected = aggregate(Infected ~ Snail, FUN=unique, data=Asher_lt)
Food = aggregate(Food ~ Snail, FUN=unique, data=Asher_lt)

snails = full_join(Infected, Food, by="Snail")
snails = full_join(snails, L_max, by="Snail")
snails = full_join(snails, C_tot, by="Snail")
snails = full_join(snails, E_tot, by="Snail")
snails = full_join(snails, Surv, by="Snail")
snails = full_join(snails, Censored, by="Snail")
snails[,"Status"] = snails[,"Status"]*3 # For AFT interval model
snails[,"First_dead"] = snails[,"Alive"] + 1
snails[,"Food"] <- factor(snails[,"Food"], levels = c("2 days", "21 days", "49 days", "Lab food"))

snails
```

```{r per_week_analysis}
snails[,"Cerc_wk"] = snails[,"Cerc"]/(snails[,"Alive"]-3)
snails[,"Egg_wk"] = snails[,"Eggs"]/(snails[,"Alive"])

Lengths = lm(Length ~ Infected*Food, data=snails)
#summary(Lengths)
contrast_matrix_L = emmeans(Lengths, pairwise ~ Food*Infected)

Eggs = lm(log(Egg_wk+1) ~ Infected*Food, data=snails)
#summary(Eggs)
contrast_matrix_E = emmeans(Eggs, pairwise ~ Food*Infected)

Cercs = lm(log(Cerc_wk+1) ~ Food, data=subset(snails, Infected=="Y"))
#summary(Cercs)
contrast_matrix_C = emmeans(Cercs, pairwise ~ Food)$emmeans

Dead = survreg(Surv(time=Alive, time2=First_dead, event=Status, type="interval") ~ Infected*Food, data=snails)
#summary(Dead)
contrast_matrix_D = emmeans(Dead, pairwise ~ Food*Infected) 

```


```{r}
contrast_groups = function(contrast_matrix){
  trts = rownames(contrast_matrix)
  group_labels = rep("", times=length(trts))
  label_letters = letters[1:length(trts)]
  which_letter = 1
  for(i in 1:(length(trts))){
    pvals = contrast_matrix[i,]
    pvals[1:i] = 0 # avoids double comparing previous treatments or itself to itself
    already_match = str_detect(group_labels, paste0("[", "z" , group_labels[i], "]"))
    new_matches = which(pvals > 0.05 & !already_match)
    if(length(new_matches) > 0){
      group_labels[c(i, new_matches)] = paste0(group_labels[c(i, new_matches)], label_letters[which_letter])
      which_letter = which_letter + 1
    }else{
      if(group_labels[i] == ""){group_labels[i] = paste0(group_labels[i], label_letters[which_letter])
      which_letter = which_letter + 1}
    }
  }
  #if(group_labels[length(trts)] == ""){group_labels[length(trts)] = label_letters[which_letter]}
  data.frame(trts, group_labels)
}

```

## Generating treatment summaries - means & SEs
```{r treatments}
# Get means and SEs
meanL = aggregate(Length ~ Food*Infected, FUN=mean, data=snails)
meanE = aggregate(Egg_wk ~ Food*Infected, FUN=mean, data=snails)
meanC = aggregate(Cerc_wk ~ Food*Infected, FUN=mean, data=snails)

SEM <- function(x){sd(x)/sqrt(length(na.omit(x)))}

SE_L = aggregate(Length ~ Food*Infected, FUN=SEM, data=snails)
SE_E = aggregate(Egg_wk ~ Food*Infected, FUN=SEM, data=snails)
SE_C = aggregate(Cerc_wk ~ Food*Infected, FUN=SEM, data=snails)

treatments = data.frame(meanL, "Length_SE" = SE_L$Length, "Eggs" =meanE$Egg_wk, "Eggs_SE" = SE_E$Egg_wk)
treatments = full_join(treatments, meanC, by=c("Food", "Infected"))
treatments = full_join(treatments, SE_C, by=c("Food", "Infected"))
treatments = rename(treatments, Cercs = Cerc_wk.x)
treatments = rename(treatments, Cercs_SE = Cerc_wk.y)
treatments[,"Infected"] = ifelse(treatments[,"Infected"] == "N", "No", "Yes")
treatments[,"Surv"] = data.frame(emmeans(Dead, pairwise ~ Food*Infected, type="response")$emmeans)$response
treatments[,"Surv_SE"] = data.frame(emmeans(Dead, pairwise ~ Food*Infected, type="response")$emmeans)$SE

treatments[,"L_labs"] = str_remove_all(cld(contrast_matrix_L, Letters=letters, sort=F)$.group, " ")
treatments[,"E_labs"] = str_remove_all(cld(contrast_matrix_E, Letters=letters, sort=F)$.group, " ")
treatments[,"C_labs"] = str_remove_all(c(rep(NA, times=4), cld(contrast_matrix_C, Letters=letters, sort=F)$.group), " ")
treatments[,"S_labs"] = str_remove_all(cld(contrast_matrix_D, Letters=letters, sort=F)$.group, " ")

treatments

```


## Building Plots

```{r plots}
pL = ggplot(data=treatments, aes(x=Food, y=Length, shape=Infected, fill=Infected)) + 
  theme(plot.margin = unit(c(0, 0.25, 0.75, 0.75), "cm")) + 
  theme(legend.position=c(0.85, 0.2), legend.title=element_text(size=10), legend.text=element_text(size=9), legend.spacing.x = unit(0, "cm"), 
        legend.spacing.y = unit(0, "cm"),
        axis.ticks.length = unit(-1.5, "mm"),
        axis.title.x = element_blank(), axis.text.x = element_blank(),
        axis.title.y = element_blank(), axis.text.y = element_text(size=8, margin = margin(r=3))) + 
  geom_linerange(aes(ymin=Length - Length_SE, ymax=Length + Length_SE), position = position_dodge(width=0.2)) +
  geom_point(position = position_dodge(width=0.2)) + geom_text(aes(label=L_labs, 
    hjust=rep(c(1, 0), each=4)), position = position_dodge(width=0.5)) +
  scale_shape_manual(values=c(21, 21)) + scale_fill_manual(values = c("white", "black")) + ylim(c(0,20))

pE = ggplot(data=treatments, aes(x=Food, y=Eggs, shape=Infected, fill=Infected)) + 
  theme(plot.margin = unit(c(0, 0.25, 0.75, 0.75), "cm")) + 
  theme(legend.position="none",
        axis.ticks.length = unit(-1.5, "mm"),
        axis.title.x = element_blank(), axis.text.x = element_blank(),
        axis.title.y = element_blank(), axis.text.y = element_text(size=8, margin = margin(r=3))) + 
  geom_linerange(aes(ymin=Eggs - Eggs_SE, ymax=Eggs + Eggs_SE), position = position_dodge(width=0.3)) +
  geom_point(position = position_dodge(width=0.3)) + geom_text(aes(label=E_labs, 
    hjust=rep(c(1, 0), each=4)), position = position_dodge(width=0.6)) +
  scale_shape_manual(values=c(21, 21)) + scale_fill_manual(values = c("white", "black")) + ylim(c(-5,60))

pC = ggplot(data=treatments, aes(x=Food, y=Cercs)) + geom_point() + geom_text(aes(label=C_labs), nudge_x = 0.15) +
  theme(plot.margin = unit(c(0, 0.25, 0.75, 0.75), "cm")) + 
  theme(legend.position="none", 
        axis.ticks.length = unit(-1.5, "mm"),
        axis.title.x = element_blank(), axis.text.x = element_blank(),
        axis.title.y = element_blank(), axis.text.y = element_text(size=8, margin = margin(r=3))) + ylim(c(0,2000)) +
  geom_linerange(aes(ymin=Cercs - Cercs_SE, ymax=Cercs + Cercs_SE)) 

pD = ggplot(data=treatments, aes(x=Food, y=Surv, shape=Infected, fill=Infected)) + 
  theme(plot.margin = unit(c(0, 0.25, 0.75, 0.75), "cm")) + 
  theme(legend.position="none",
        axis.ticks.length = unit(-1.5, "mm"),
        axis.title.x = element_blank(), axis.text.x = element_text(size=8, margin = margin(t=3)),
        axis.title.y = element_blank(), axis.text.y = element_text(size=8, margin = margin(r=3))) + 
  geom_linerange(aes(ymin=Surv - Surv_SE, ymax=Surv + Surv_SE), position = position_dodge(width=0.3)) +
  geom_point(position = position_dodge(width=0.3)) + geom_text(aes(label=S_labs, 
    hjust=rep(c(1, 0), each=4)), position = position_dodge(width=0.6)) +
  scale_shape_manual(values=c(21, 21)) + scale_fill_manual(values = c("white", "black")) +
  scale_x_discrete(labels =  c("2 days", "21 days", "49 days", "Lab\nfood"))


```


```{r plot_grid}
Fig2 = plot_grid(pL, pE, pC, pD, align="v", ncol=1, nrow=4, axis="rltb", scale=1) +
  # y-axis labels
  draw_label("Final length, mm ± SE", x=0.04, y=0.9, angle=90, size=10) +
  draw_label("Weekly reproduction\nrate ± SE", x=0.04, y=0.65, angle=90, size=10) +
  draw_label("Cercarial production\nrate ± SE", x=0.04, y=0.45, angle=90, size=10) +
  draw_label("Estimated Median\nsurvival, weeks ± SE", x=0.04, y=0.15, angle=90, size=10) +
  # x-axis labels
  draw_label("Food resource", x = 0.55, y = 0.02, size=10) +
  # panel labels
  draw_label("A", x = 0.2, y = 0.99, size=10) + 
  draw_label("B", x = 0.2, y = 0.75, size=10) +
  draw_label("C", x = 0.2, y = 0.5, size=10) +
  draw_label("D", x = 0.2, y = 0.25, size=10)

setwd("C:/RData")
save_plot("Fig2_Detritus.png", Fig2, ncol=1, nrow=3, base_height=2, base_aspect_ratio = 1.75, dpi=600, units="in")

```

